High Resolution Identification of Protein-DNA Binding Events and Quality Control for ChIP-exo data

### 2016-02-25 rmarkdown/paper.Rnw
most of the paper done, methods missing + conclusions

\listoffigures

\listoftables

@@

We calculated the most commonly used quality indicators (list in table
\ref{tab:qc}) for ChIP-Seq data using all the ChIP-exo data we
gathered. The PCR Bottleneck Coefficient (PBC) and the Normalized
Strand Cross-Correlation (NSC) are calculated as in \cite{encode_qc}.
Additionally, we calculated the Forward Strand Ratio (FSR) to comped
the number of fragments sequenced from each strand. We can observe
that the PBC is low, hence it would be incorrectly suggested to repeat
the experiment.

\begin{table}[H]
  \centering
  \caption{Usual quality control indicators applied to the gathered ChIP-exo samples. 
    PBC stands for PCR Bottleneck Coefficient, NSC for Normalized Strand Cross-Correlation and
    FSR for Forward Strand Ratio. We ommited the Relative Strand Cross-Correlation (RSC) because
    a typical ChIP-exo experiment is not accompanied by an input file.}
  \label{tab:qc}
\end{table}

@@

>>>>

@@

We started our exploration by investigating the suitability of the
current state-of-the-art QC pipelines for ChIP-Seq for ChIP-exo. Table
\ref{tab:qc} contains measures that are commonly calculated for
ChIP-Seq samples: PCR Bottleneck Coefficient (PBC) and the Normalized
Strand Cross-Correlation (NSC) are calculated as in \cite{encode_qc}.
Additionally, we calculated the Forward Strand Ratio (FSR) to comped
the number of fragments sequenced from each strand.

%% We can observe that the PBC is low, hence it would be incorrectly
%% suggested to repeat the experiment.

\begin{table}[h!]
%% need to fix format
  \centering
<<table1,include = TRUE,echo = FALSE,eval = TRUE>>=
  load("../data/paper_tables/Landick_rif_summary.RData")
  load("../data/paper_tables/Landick_aero_summary.RData")
  load("../data/paper_tables/pugh_ctcf.RData")
  load("../data/paper_tables/Carroll_mm9_FoxA1.RData")
  load("../data/paper_tables/Meijsing_hg19_GR.RData")
  load("../data/paper_tables/Carroll_hg19_ER.RData")
  do.call(rbind,list(landick_aero,
                     landick_rif,
                     pugh_ctcf,
                     carroll_mm9_FoxA1,
                     meijing_hg19_GR,
                     carroll_hg19_ER))
@ 
\caption{Usual quality control indicators applied to the gathered
  ChIP-exo samples.  PBC stands for PCR Bottleneck Coefficient (0 -
  0.5 is severe bottlenecking, 0.5 - 0.8 is moderate bottlenecking,
  0.8 - 0.9 is mild bottlenecking, while 0.9 - 1 is no bottlenecking),
  NSC for Normalized Strand Cross-Correlation and FSR for Forward
  Strand Ratio. We omitted the Relative Strand Cross-Correlation (RSC)
  because a typical ChIP-exo experiment is not accompanied by an input
  file. $\sig$ samples were given by Dr. Landick's Lab, FoxA1 and ER
  samples are from Serandour et al., 2013 \cite{exoillumina} and CTCF
  sample is from Rhee and Pugh, 2011 \cite{exo1}}
  \label{tab:qc} %% need to make this table
\end{table}

It is of special importance to notice that the values of PBC are quite
low, hence it would be necessary to repeat these experiments by
following ChIP-seq guidelines. On the other hand, in a good ChIP-Seq
experiment the SCC is maximized at the fragment length, and a
``phantom peak'' would be also present at the experiment's read length
(\cite{encode_qc} and \cite{strandcc}). However, in ChIP-exo's case
these two peaks are confounded. Hence an enrichment measure based in
SCC such as the NSC is harder to interpret. In figure
\ref{fig:scc_exo} we observe that both local maxima are hard to
differentiate in the SCC curves for the $\sig$ ChIP-exo datasets used to
calculate the NSC values in table \ref{tab:qc}.

% % According to ENCODE's quality metrics, NSC values close
% % to one corresponds to low enrichment samples or bad quality datasets

\subsection{Comparison with ChIP-Seq data}

<<comp_param , include = FALSE,echo = FALSE,eval = TRUE>>=

  bin_size <- 150
  frag_len <- 150

@

We first compared various factors that could affect binding site
identification between ChIP-exo and ChIP-Seq data. In order to compare
distribution of signal and background between ChIP-exo and ChIP-Seq
data, we calculated ChIP tag counts across the genome by counting the
number of reads mapping to each of \Sexpr{bin_size} non-overlapping
window after extending reads by \Sexpr{frag_len} to their 3' end
directions. ChIP tag counts in ChIP-exo data were linearly related to
ChIP tag counts in ChIP-Seq data for the regions with high ChIP tag
counts (Figure \ref{fig:comp}A). This implies that signals for
potential binding sites are well reproducible between ChIP-exo and
ChIP-Seq data. On the other hand, there was clear difference in the
background distribution between them. In ChIP-Seq data reads were
almost uniformly distributed over background (non-binding) regions and
the ChIP tag counts in there regions were significantly larger than
zero. In contrast, in ChIP-exo data, there was larger variation in
ChIP tag counts among background regions and ChIP tag counts were much
lower in these regions compared to ChIP-Seq data. There were also
large proportion of regions without any read in ChIP-exo data. These
results indicate that for ChIP-exo data a much smaller portion of the
genome is expected to be background.

We next evaluated the ``peak pair'' assumption from Rhee and Pugh,
2011 \cite{exo1}, i.e. a peak of reads in the forward strand is
usually paired with a peak of reads in the reverse strand that is
located in the other site of the binding site. Wang et al., 2014
\cite{mace}, Madrigal 2015 \cite{cexor} and Bardet et al., 2013
\cite{peakzilla} proposed method rely in this assumption. In order to
evaluate this assumption, we reviewed the proportion of reads in the
forward strand in candidate regions (i.e. regions with at least one
binding site) in $\sig$ ChIP-exo data. We found that strands of reads
were much less balanced in ChIP-exo data than in ChIP-Seq data in
these regions with potential binding sites (Fig. \ref{fig:comp}B) and
this indicates that the peak pair assumption might not hold in real
ChIP-exo data.

We evaluated ChIP-exo data for CTCF factor from human genome
\cite{exo1} to investigate issues specific to eukaryotic genomes for
binding sites identification. Figures \ref{fig:comp}C and
\ref{fig:comp}D display the bin-level average read counts against
mappability and GC content. Each data point is obtained by averaging
the read counts across bins with the same mappability of GC
content. These results indicate that binding site identification in
ChIP-exo sample might also benefit from the use of methods that take
into account of apparent sequence biases such as mappability and GC
content.

\subsection{ChIP-exo Quality Control Pipeline}

Figure \ref{fig:qcdiagram} shows a flowchart for the ChIP-exo QC
pipeline. Which basically partitions the genome by keeping the
non-digested ChIP-exo regions. Then, for each region calculates a
series of summary statistics. Finally it creates several
visualizations designed to assess the quality level of ChIP-exo
sample.

\subsubsection{Enrichment and library complexity in ChIP-exo data}

In ChIP-exo experiments, the background is often digested by the
exonuclease enzyme, therefore to determine the sample's quality is
necessary to address the balance between the enrichment and library
complexity of an experiment. To diagnose this, we considered the
Average Read Coverage (ARC) and the Unique Read Coverage Rate (URCR)
which are defined as follows:

\begin{align*}
  \text{ARC} &= \dfrac{\text{Nr. of reads in the region}}{\text{Width of the region}} \\
  \text{URCR} &= \dfrac{\text{Nr. of reads in the region mapped to exactly one position}}{\text{Nr. of reads in the region}} 
\end{align*}

Using the FoxA1 in mouse liver cell lines from \cite{exoillumina} and
these two quantities, the relationship between library complexity and
experiment enrichment was explored. In figure \ref{fig:enrich}A we can
observe both statistics for the regions that are common for the three
replicates. This figure shows typical patterns for ChIP-exo
experiment, there are two strong arms: The one on the left with low
ARC and varying URCR corresponds to ChIP-exo's background, usually
regions composed by scattered reads that were not digested during the
exonuclease step; and the one on the right that corresponds to regions
that are usually enriched, for these regions the URCR measures how the
fragments are allocated into the possible positions in a region. Hence
we would expect the first replicate to have have more enriched regions
and the third replicate's library complexity to be lower than the
other two replicates library complexities. To verify this statements,
we extracted the sequences around high confidence binding events and
look for the FoxA1 motif using FIMO \cite{fimo}. Figure
\ref{fig:enrich}B shows the number of candidate regions, which shows
that the first replicate is being allocated into more enriched regions
than the other ones. Figure \ref{fig:enrich}C shows that for the first
and third replicates, the FoxA1 motif is being detected in roughly the
same proportion of sites, and finally in \ref{fig:enrich}D we observe
that the first and third replicate can detect the FoxA1 motif with the
same significance, while the second replicate does not.

\subsubsection{Strand imbalance in ChIP-exo data}

The strand imbalance assessment in based in the observation that the
enriched regions usually are composed of a higher quantity of reads,
therefore we examined the FSR (defined as the ratio of number of
forward stranded reads divided by the total number of reads in a given
region) as the regions with lower depth are being filtered out. This
indicator is of particular importance, since several methods rely on
the ``peak-pair'' assumption. In table \ref{tab:qc}, we calculated the
global FSR and noticed that for all experiments is roughly $0.5$,
which means there are roughly the same amount of reads in both
strands. However figure \ref{fig:strand} shows that the global FSR
does not represent the experiment's local strand imbalance, hence the
``peak pair'' assumption may not hold well in real ChIP-exo data.

In order to asses the strand imbalance we created the visualization
shown in figure \ref{fig:strand}: Figure \ref{fig:strand}A presents
the FSR's behavior as the lower depth regions are being filtered out,
while B) shows which percentage of the regions are composed by reads
in both strand or only one (forward or backward). In a good data set,
it would be expected that all quantiles shown to be quickly converging
towards the median (in panel A) or the regions composed of reads in
one strand being made of few fragments (in panel B). For each
replicate, we divided the partitioned regions by asking whether they
overlap a set of high quality ChIP-exo peaks, and then we tested if
the strand imbalance's distribution were the same for both
classes. For regions composed by a higher amount of reads, is is
harder to distinguish their peaks by considering only the strand
imbalance, and in an experiment with lower quality it is harder to
make this distinction.

\subsection{Comparison with ChIP-Seq data using dPeak}

<<comp_param,include = FALSE,echo = FALSE, eval = TRUE>>=

  id_dist <- 20
  ext <- 15

@

Figure \ref{fig:reso_all} shows different comparisons among ChIP-exo,
PE ChIP-Seq and SE ChIP-Seq. A RegulonDB annotation (Salgado et al,
2012 \cite{regulondb}) was considered identified if the distance
between it and a dPeak binding site estimate was at most of
$\Sexpr{id_dist}$ bp. That way, the sensitivity is defined as the
proportion of RegulonDB annotations identified in a peak and the
resolution is defined as the minimum distance between a RegulonDB
annotation and the dPeak binding site estimates. The left panel of
figure \ref{fig:reso_all} shows that the sensitivity increases as the
mean distance between binding events increases. Despite the when the
binding events in a peak are closer to each other, both ChIP-exo and
PE ChIP-Seq are comparable, as the distance increases ChIP-exo
identifies a higher proportion of the RegulonDB annotations;
additionally SE ChIP-Seq is significantly less sensitive than both
ChIP-exo and PE ChIP-Seq. The right panel shows that ChIP-exo and PE
ChIP-Seq are comparable in resolution, while both protocols
significantly outperform SE ChIP-Seq.

\subsection{Systematic comparison of ChIP-Seq vs ChIP-exo under varying sequencing depth}

Previously, ChIP-exo and SE ChIP-Seq have been compared at a fixed
depth level in the literature, but this comparisons did not include PE
ChIP-Seq. Hence, we sampled a fixed amount of reads for each of the
ChIP-exo, PE ChIP-Seq and SE ChIP-Seq datasets of the $\sig$
samples. For each sampled dataset we applied out lower-to-higher
resolution pipeline by calling peaks with MOSAiCS \cite{mosaics} and
then deconvolving the binding events by using dPeak \cite{dpeak}. For
the ChIP-exo datasets we called peaks by using the GC-content and
mappability models with MOSAiCS, and for the ChIP-Seq datasets we used
their respective Input samples.

Figures \ref{fig:design} shows the behavior of each data type in
$\sig$ experiment under aerobic condition when their depth is
fixed. It is remarkable that even when the number of candidate peaks
or the number of predicted events is lower for ChIP-exo, it
outperforms both PE and SE ChIP-Seq in number of identified targets
and resolution.

This may suggest that with ChIP-exo less positive peaks are being
called and that when the targets are being identified, dPeak estimates
binding locations closer to the true location. Additionally, we can
see that as the read depth increases, all four indicator seem to
stabilize and hit a plateau, which may indicate that with ChIP-exo a
smaller amount of reads is necessary to identify a higher number of
targets, but it may be also possible that this is an artifact occurring
due to ChIP-exo's lower library complexity. Additionally, it is worth
noting that for PE ChIP-Seq we sampled both ends of the fragment,
hence for each sequencing depth we are sampling the half amount of
pairs for PE ChIP-Seq than for ChIP-exo or SE ChIP-Seq.

Figure \ref{fig:saturation_rif} shows an analogous analysis but using
the $\sig$ replicates with and without rif treatment. The left, middle
and right columns shows the fixed depth against the number of
predicted events, identified targets and resolution being compared at
a fixed depth level. The behavior of this quantities seems to be
opposite to the one as in figure \ref{fig:design}, hence we used the
ChIP-exo QC pipeline in the fixed depth ChIP-exo experiments. Figure
\ref{fig:exoQC_sat_aero} shows hexbin of ARC vs URCR for several fixed
sample sizes, as the fixed depth increases the two arm pattern becomes
more distinctive while for lower depth, it seems that the majority of
the sampled reads were aligned to enriched regions. On the other hand
in figures \ref{fig:exoQC_sat1} to \ref{fig:exoQC_sat4}, we used the
ChIP-exo QC pipeline on the samples that are outperformed by PE and SE
ChIP-Seq. For a fixed low depth, we can see that the majority of the
reads are being aligned to non-enriched regions since the vertical arm
seems to be stronger for all 2 conditions and replicates; for higher
depth we can see low URCR values being predominant, which indicates
that the majority of the regions being formed by few positions with a
higher read concentration. In low complexity regions, the reads are
being aligned to fewer positions but there is no control over the
amount of reads mapped. Hence, those regions are more likely to being
strand-imbalance which in turn may bias the binding site estimate and
therefore decrease the number of identified targets or increase an
experiments resolution.

% In supplement figures \ref{fig:exoQC_sat1} to \ref{fig:exoQC_sat4}, we
% repeat the same analysis for both replicates under the two rif
% conditions.

\subsection{dPeak outperforms competing methods in discovering closely
  spaced binding events from ChIP-exo and ChIP-Seq data}

Figure \ref{fig:methods_comp} compares the resolution defined as the
minimum distance between a RegulonDB annotation and a binding site
predicted by either Peakzilla \cite{peakzilla}, MACE \cite{mace}, GEM
\cite{gem} or dPeak \cite{dpeak}. In a good dataset such as both of
the ChIP-exo experiments under aerobic (panel 933) or anaerobic (panel
931) conditions, all the methods are comparable in resolution, and
dPeak slightly outperforms the rest. On the other hand, for
experiments with low library complexity the resolution calculated with
dPeak's predictions is smaller than both Mace and Peakzilla, but it is
greater than Gem. This may be due to the fact that Gem uses sequence
information in addition to the 5' ends counts per coordinate that
dPeak uses. \footnote{For here we may probably use only 933 as part of
  the main article and keep the rest for the supplement}

\section{Methods}
\label{sec:methods}

@@

\section{Figures}

\begin{figure}[h!]
\centering
\includegraphics[width = .8\textwidth]{/p/keles/ChIPexo/volume3/ChIPexo/figs/for_paper/EColi_strand_cross_corr.pdf}
  \caption{SCC curves for $\sig$ samples. The ``phantom peak'' and the
    summit that corresponds to the read and fragment length
    respectively are confounded due to the exonuclease digestion.}
  \label{fig:scc_exo}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width = .46\textwidth,page = 3 ]{../figs/for_paper/ChIPseqPET_ChIPexo_tagCount_comparison.pdf}
  \includegraphics[width = .46\textwidth]{../figs/for_paper/forward_strand_ratio_comp_old.pdf}
\includegraphics[width = .46\textwidth,page = 1]{../figs/for_paper/eukaryotic_bias_CTCF.pdf}
  \includegraphics[width = .46\textwidth,page = 2]{../figs/for_paper/eukaryotic_bias_CTCF.pdf}
  \caption{ A) Hexbin plot of PE ChIP-Seq bin counts VS ChIP-exo bin
    counts. B) Forward Strand Ratio densities for SE ChIP-Seq and
    ChIP-exo peaks. C) ChIP tag counts increase linearly as
    mappability scores increases. D) ChIP tag counts increase linearly
    as GC content score increases when GC content is less than 0.6 and
    then ChIP tag counts decrease as GC content increases. D)
    Percentage of sites with at least p.value.}
  \label{fig:comp}
\end{figure}

\begin{figure}[h!]
  \centering
  \centering
  \includegraphics[width = \textwidth]{../figs/for_paper/coverage_diagram2.pdf}
  \caption{Flowchart of the ChIP-exo quality control pipeline.}
  \label{fig:qcdiagram}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width = .9  \textwidth,page = 1]{../figs/Carroll_mice_for_paper/FoxA1_enrichment.pdf}
  \newline
  \includegraphics[width = .3 \textwidth,page = 1]{../figs/FOXA1_mm9_fimo/FOXA1_summaries_by_replicate.pdf}
  \includegraphics[width = .3 \textwidth,page = 3]{../figs/FOXA1_mm9_fimo/FOXA1_summaries_by_replicate.pdf}
  \includegraphics[width = .3 \textwidth,page = 1]{../figs/FOXA1_mm9_fimo/FOXA1_log10pval_cumulative_nmotifs.pdf}
  \caption{Using the mouse-FoxA1 experiment from \cite{exoillumina}:
    A) Hexbin plots of $\mbox{ARC}$ against $\mbox{URCR}$, in general
    we can see a slight separation into two strong arms, one
    corresponds to low $\mbox{ARC}$ and varying $\mbox{URCR}$, and for
    the other $\mbox{URCR}$ decreases as $\mbox{ARC}$ increases. B)
    Number of candidate sites for each replicate. C) Percentage of
    candidate sites where the FoxA1 motif was detected. D) 
 }
  \label{fig:enrich}
\end{figure}

\begin{figure}[h!]
  \centering  
  \includegraphics[width = .9\textwidth,page = 1]{../figs/Carroll_mice_for_paper/Strand_imbalance.pdf} 
  \newline
  \includegraphics[width = .9\textwidth,page = 2]{../figs/Carroll_mice_for_paper/Strand_imbalance.pdf} 
  \includegraphics[width = .4\textwidth]{../figs/for_paper/Carroll_FSR_depth_VS_pvalWilcoxon.pdf}
  \caption{Strand imbalance QC plots for the same data as in Figure
    \ref{fig:enrich}A. A) FSR distribution quantiles as the lower
    depth regions are being filtered out, all quantiles approach to
    the median as the lower bound increases. B) Stacked histogram with
    the proportion of regions that are formed by two strands or only
    one, in a good sample the single-stranded regions are going to be
    filtered out quickly as in the middle row. C)
    $-log_{10}(\text{p.value})$ of testing if the imbalance
    distributions differs when ChIP-exo regions overlap their peaks.}
  \label{fig:strand}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width = .46\textwidth]{../figs/for_paper/sensitivity_exo_olda_data.pdf}
  \includegraphics[width = .46\textwidth]{../figs/for_paper/resolution_by_dataset_old_data.pdf}
   \caption{Comparison of (A) sensitivity and (B) resolution between
     ChIP-exo and ChIP-Seq data. Sensitivity is defined as the
     proportion of RegulonDB annotations identified using each
     data. Resolution is defined as the distance between RegulonDB
     annotation and its closest prediction.}
  \label{fig:reso_all}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width = .9\textwidth]{../figs/for_paper/saturation_analysis_old.pdf}
  \caption{\textbf{ChIP-exo, PE ChIP-Seq and SE ChIP-Seq comparison at
      varying sequencing depths.} Comparison of the number of candidate
    regions (A), predicted events (B), identified targets (C) and
    resolution (D) among ChIP-exo, PE ChIP-Seq and SE
    ChIP-Seq. RegulonDB annotations are considered as a gold
    standard. A gold standard binding events was deemed identified if
    a binding event was estimated at a $\pm$ \Sexpr{ext} vicinity of
    it.}
  \label{fig:design}
\end{figure}

\begin{figure}[h!]
  \centering
\includegraphics[width = .9\textwidth]{../figs/saturation/K12_alignment/sig70_aerobic_enrichment.pdf}
\caption{Hexbin plots of ARC vs URCR of the $\sig$ ChIP-exo experiment
  under aerobic condition when 10K to 90K reads are being sampled.}
  \label{fig:exoQC_sat_aero}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width = .9\textwidth]{../figs/for_paper/sig70_methods_comparison_FDR5_topM300.pdf}
  \caption{Comparison of the resolution between dPeak, Gem, Mace and
    Peakzilla methods. Resolution is defined as the minimum distance
    between a RegulonDB annotation an a predicted binding event.}
  \label{fig:methods_comp}
\end{figure}

\section*{Supplement}
\label{sec:supp}

\begin{table}[h!]
%% need to fix format
  \centering
<<table_chipseq,include = TRUE,echo = FALSE,eval = TRUE>>=
  load("../data/paper_tables/Landick_rif_chipseq_summary.RData")
  do.call(rbind,chipseq)
@ 
\caption{Same QC metrics as in table \ref{tab:qc} but applied to
  Landick's chipseq data of the rif experiment}
\end{table}

\begin{figure}[h!]
  \centering % note change to stat_density(geom = "line")
   \includegraphics[width = .46\textwidth,page = 1]{../figs/for_paper/sigma_delta_old_densities.pdf}
   \includegraphics[width = .46\textwidth,page = 2]{../figs/for_paper/sigma_delta_old_densities.pdf}   
  \caption{ C) $\delta$ parameter in dPeak measures average distance
    of the reads to their respective binding site. In ChIP-exo data,
    reads were located much closer to the binding site than in SET
    ChIP-Seq. D) $\sigma$ parameter measure the dispersion of reads
    around each binding site. In ChIP-exo data, reads showed less
    variation around the their respective binding sites compared to
    SET ChIP-Seq.}

\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width = .7\textwidth]{../figs/saturation/K12_alignment/PBC_saturation.pdf}
  \caption{Average PBC (among all seeds) of the sampled ChIP-exo, PE
    ChIP-Seq and SE ChIP-Seq experiments under the rif treatment
    conditions used for saturation analysis.}
  \label{fig:pbc_saturation}
\end{figure}

\begin{figure}[h!] %%% fix this plot as one ggplot, facet_grid(condition ~ variable,scales = "free_y")
  \centering
  \begin{itemize}
  \item Rep-1 and rif-0min:
  \end{itemize}
  \includegraphics[width = .3\textwidth,page =2]{../figs/saturation/K12_alignment/Sig70_rep1_rif0_saturation_analysis.pdf}
  \includegraphics[width = .3\textwidth,page =3]{../figs/saturation/K12_alignment/Sig70_rep1_rif0_saturation_analysis.pdf}
  \includegraphics[width = .3\textwidth,page =4]{../figs/saturation/K12_alignment/Sig70_rep1_rif0_saturation_analysis.pdf}

  \begin{itemize}
  \item Rep-1 and rif-20min:
  \end{itemize}

  \includegraphics[width = .3\textwidth,page =2]{../figs/saturation/K12_alignment/Sig70_rep1_rif20_saturation_analysis.pdf}
  \includegraphics[width = .3\textwidth,page =3]{../figs/saturation/K12_alignment/Sig70_rep1_rif20_saturation_analysis.pdf}
  \includegraphics[width = .3\textwidth,page =4]{../figs/saturation/K12_alignment/Sig70_rep1_rif20_saturation_analysis.pdf}

  \begin{itemize}
  \item Rep-2 and rif-0min:
  \end{itemize}

  \includegraphics[width = .3\textwidth,page =2]{../figs/saturation/K12_alignment/Sig70_rep2_rif0_saturation_analysis.pdf}
  \includegraphics[width = .3\textwidth,page =3]{../figs/saturation/K12_alignment/Sig70_rep2_rif0_saturation_analysis.pdf}
  \includegraphics[width = .3\textwidth,page =4]{../figs/saturation/K12_alignment/Sig70_rep2_rif0_saturation_analysis.pdf}

  \begin{itemize}
  \item Rep-2 and rif-20min:
  \end{itemize}

  \includegraphics[width = .3\textwidth,page =2]{../figs/saturation/K12_alignment/Sig70_rep2_rif20_saturation_analysis.pdf}
  \includegraphics[width = .3\textwidth,page =3]{../figs/saturation/K12_alignment/Sig70_rep2_rif20_saturation_analysis.pdf}
  \includegraphics[width = .3\textwidth,page =4]{../figs/saturation/K12_alignment/Sig70_rep2_rif20_saturation_analysis.pdf}
  \caption{\textbf{ChIP-exo, PE ChIP-Seq and SE ChIP-Seq comparison at
      varying sequencing depth} Comparison of the number of predicted
    events (left), identified targets (middle) and resolution (right)
    among ChIP-exo, PE ChIP-Seq and SE ChIP-Seq. RegulonDB annotations
    are considered as gold standard. A RegulonDB binding events was
    deemed identified if a binding event was estimated at a $\pm$ \Sexpr{ext}
    vicinity of it.}
  \label{fig:saturation_rif}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width = .9\textwidth,page = 1]{../figs/saturation/K12_alignment/sig70_rif_enrichment.pdf}
  \caption{A) ARC vs URCR hexbin plots of Rep-1 and rif-0min from $\sig$ experiment when 100K to 900K reads are being
    sampled for each panel. }
  \label{fig:exoQC_sat1}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width = .9\textwidth,page = 1]{../figs/saturation/K12_alignment/sig70_rif_enrichment.pdf}

  \caption{ARC vs URCR hexbin plots of Rep-1 and rif-20min from $\sig$ experiment when 100K to 900K reads are being
    sampled for each panel.}
  \label{fig:exoQC_sat2}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width = .9\textwidth,page = 1]{../figs/saturation/K12_alignment/sig70_rif_enrichment.pdf}
  \caption{ARC vs URCR hexbin plots of Rep-2 and rif-0min from $\sig$ experiment when 100K to 900K reads are being
    sampled for each panel.}
  \label{fig:exoQC_sat3}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width = .9\textwidth,page = 1]{../figs/saturation/K12_alignment/sig70_rif_enrichment.pdf}
  \caption{ARC vs URCR hexbin plots of Rep-2 and rif-20min from $\sig$ experiment when 100K to 900K reads are being
    sampled for each panel.}
  \label{fig:exoQC_sat4}
\end{figure}
